Exploring probability distributions for bivariate temporal granularities

### 2019-12-05 main.Rmd
density estimation section

The measured variable can be dicrete or continuous. The probability distribution of these univariate measured variable could be studied by estimating the probability density function (pdf for continuous) or probability mass function (pmf for dicrete). Both pdf and pmf are concerned with point probabilities of the random variable. Suppose we have observations which are realizations of univariate random variables, $X_1, X_2, \dots, X_n \sim F$, where $F$ denotes an unknown cumulative distribution function and $X_1, X_2, \dots, X_n$ are i.i.d. The densities can either be estimated or summarized using quantiles.Instead of assuming a parametric model for the distribution (e.g. a Normal distribution with unknown expectation and variance), a non-parametric estimation assumes that the density exists and is suitably smooth (e.g. differentiable). It is then possible to estimate the unknown density function f(·).

>>>>

Density estimates are ueful in investigation of the properties of the measured variable. They can give valuable indication of features like skewness, multimodality or tail behavior. The measured variable can be dicrete or continuous. The probability distribution of these univariate measured variable could be studied by estimating the probability density function (continuous) or probability mass function (dicrete). The densities can either be estimated or summarized using empirical quantiles. The approach can be parametric or non-parametric. A non-parametric approach makes less rigid assumptions about the distribution of the observed data making the data speak more for itself.

The most commonly used density estimation method is the kernel density estimator. The Kernel density estimator with Kernel K is defined by:

$$\hat{f(x)} = (1/nh)\sum_{i=1}^{n} K(x-X_i)/h$$ , where $h$ is the smoothing parameter or the bandwidth. where $X_1, X_2, \dots, X_n \sim F$ are independent and identically distributed observations from a continuous univariate distribution with probabilitty density function f(·).

 <!-- Both pdf and pmf are concerned with point probabilities of the random variable. Suppose we have observations which are realizations of univariate random variables, $X_1, X_2, \dots, X_n \sim F$, where $F$ denotes an unknown cumulative distribution function and $X_1, X_2, \dots, X_n$ are i.i.d. -->

<!-- Instead of assuming a parametric model for the distribution (e.g. a Normal distribution with unknown expectation and variance), a non-parametric estimation assumes that the density exists and is suitably smooth (e.g. differentiable). It is then possible to estimate the u2nknown density function f(·). -->
